Analysis of Physical Activity Survey(2022)

### 2023-02-14 outputs/paper/paper.Rmd
Minor adjustments, changed graph labels, and table positions.

---
title: "Analysis of Physical Activity Survey(2022)"
author: 
  - Jonathan Goodwin
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Recreational activity and physical fitness are important factors in determining the health and safety of a society. We obtain data regarding the activity of individuals of different states and age groups as well as their respective distance to a park. We find that citizens who live closer to parks are more likely to be physically active, and that younger citizens are more likely to be physically active then older ones. These findings have implications for the future development of public recreational structures."
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H}
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
```{r setup, include=FALSE,warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message= FALSE, fig.pos = 'H')
library(tidyverse)
library(kableExtra)
library(reshape2)
```
```{r, echo = F}
### Reading CSV and setting seed###
set.seed(1)
Data <- 
  read.csv(here::here("outputs/data/cleaned_physical_activity.csv"))
Data1 <- read.csv(here::here("outputs/data/cleaned_walk_or_bike.csv"))
```

@@

```{r fig1, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df1 <- subset(df, Year == 2011)
df1 <- subset(df1, Question == "Percent of adults aged 18 years and older who have obesity")
df1 <- df1[order(df1$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df1[i,4],df1[i+1,4],df1[i+2,4],df1[i+3,4],df1[i+4,4],df1[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means <- cbind(unique(df1$Year),unique(df1$State), unique(df1$Question), round(x, digits = 1))
df_means <- as.data.frame(df_means)
df_long <- melt(df_means[order(df_means$V4),])
p <- ggplot(df_long, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,35)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("State") +
  ylab("Percent of Population")

Below Table \@ref(tab:tab2), shows the states with the lowest proportions of obesity.

```{r tab2, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means2 <- df_means[order(df_means$V4),]
names(df.means2)[names(df.means2) == 'V2'] <- 'State'
names(df.means2)[names(df.means2) == 'V4'] <- 'Proportion'
df.new <- cbind(df.means2$State,df.means2$Proportion)
knitr::kable(head(df.new),booktabs = TRUE, align = "c", caption = "Lowest Obesity Rates By State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

And here Table \@ref(tab:tab3) gives the states with the highest obesity rates.

```{r tab3, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means3 <- df_means[order(df_means$V4, decreasing = T),]
names(df.means3)[names(df.means3) == 'V2'] <- 'State'
names(df.means3)[names(df.means3) == 'V4'] <- 'Proportion'
df.new2 <- cbind(df.means3$State,df.means3$Proportion)
knitr::kable(head(df.new2),booktabs = TRUE, align = "c", caption = "Highest Obesity Rates by State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r fig2, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df2 <- subset(df, Year == 2019)
df2 <- subset(df2, Question == "Percent of adults aged 18 years and older who have obesity")
df2 <- df2[order(df2$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df2[i,4],df2[i+1,4],df2[i+2,4],df2[i+3,4],df2[i+4,4],df2[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_m <- cbind(unique(df2$Year),unique(df2$State), unique(df2$Question), round(x, digits = 1))
df_m <- as.data.frame(df_m)
df_l <- melt(df_m[order(df_m$V4),])
p <- ggplot(df_l, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,50)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("State") +
  ylab("Percent of Population")

@@

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Lowest Rates of Obesity by State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab5, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means5 <- df_m[order(df_m$V4, decreasing = T),]
names(df.means5)[names(df.means5) == 'V2'] <- 'State'
names(df.means5)[names(df.means5) == 'V4'] <- 'Proportion'
df.new5 <- cbind(df.means5$State,df.means5$Proportion)
knitr::kable(head(df.new5),booktabs = TRUE, align = "c", caption = "Highest Rates of Obesity by State") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

Below we now look at the proportion of state residents participating in aerobic activities for 150min or more per week as well as the proportion of residents participating in muscle strength training for at least 2 hours per week. We see in Table \@ref(tab:tab10) and Table \@ref(tab:tab11) some familiar states from the Obesity rate Tables \@ref(tab:tab4) and Table \@ref(tab:tab5). Namely Alabama which was one of the highest rates for Obesity in the country also has low rates of Aerobic activity.
```{r tab10, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means4 <- df8_means_150[order(df8_means_150$V4),]
names(df8.means4)[names(df8.means4) == 'V2'] <- 'State'
names(df8.means4)[names(df8.means4) == 'V4'] <- 'Proportion'
df8.new4 <- cbind(df8.means4$State,df8.means4$Proportion)
knitr::kable(head(df8.new4),booktabs = TRUE, align = "c", caption = "States with Lowest rates of Aerobic training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab11, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means5 <- df8_means_150[order(df8_means_150$V4, decreasing = T),]
names(df8.means5)[names(df8.means5) == 'V2'] <- 'State'
names(df8.means5)[names(df8.means5) == 'V4'] <- 'Proportion'
df8.new5 <- cbind(df8.means5$State,df8.means5$Proportion)
knitr::kable(head(df8.new5),booktabs = TRUE, align = "c", caption = "States with Highest rates of Aerobic training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r tab12, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means6 <- df8_means_muscle[order(df8_means_muscle$V4),]
names(df8.means6)[names(df8.means6) == 'V2'] <- 'State'
names(df8.means6)[names(df8.means6) == 'V4'] <- 'Proportion'
df8.new6 <- cbind(df8.means6$State,df8.means6$Proportion)
knitr::kable(head(df8.new6),booktabs = TRUE, align = "c", caption = "States with Lowest rates of Muscle Training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab13, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means7 <- df8_means_muscle[order(df8_means_muscle$V4, decreasing = T),]
names(df8.means7)[names(df8.means7) == 'V2'] <- 'State'
names(df8.means7)[names(df8.means7) == 'V4'] <- 'Proportion'
df8.new7 <- cbind(df8.means7$State,df8.means7$Proportion)
knitr::kable(head(df8.new7),booktabs = TRUE, align = "c", caption = "States with Highest rates of Muscle training") %>% 
kable_styling(full_width = F) %>%
kable_styling(latex_options = "HOLD_position")
```
The interesting thing here is we see Montana and Vermont both with very high rates of Aerobic Activity, likely attributed to these states being far more rural then the average state, allowing more opportunity for outdoor activities. However again on the low end 
\newpage

>>>>

---
title: "Analysis of Physical Activity Survey(2022)"
author: "Jonathan Goodwin"
date: "2022 March 7"
output:
  html_document: default
  bookdown: default
  pdf_document: default
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
abstract: Recreational activity and physical fitness are important factors in determining
  the health and safety of a society. We obtain data regarding the activity of individuals
  of different states and age groups as well as their respective distance to a park.
  We find that citizens who live closer to parks are more likely to be physically
  active, and that younger citizens are more likely to be physically active then older
  ones. These findings have implications for the future development of public recreational
  structures.
toc: no
bibliography: references.bib
---
```{r setup, include=FALSE,warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message= FALSE, fig.pos = 'H')
library(tidyverse)
library(kableExtra)
library(reshape2)
library(here)
```
```{r, echo = F}
### Reading CSV and setting seed###
set.seed(1)
Data <- 
  read.csv(here::here("outputs/data/cleaned_physical_activity.csv"))
Data1 <- read.csv(here::here("outputs/data/cleaned_walk_or_bike.csv"))
```

@@

```{r fig1, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8, messages = FALSE}
### Bar plot of Obesity by State ###
df1 <- subset(df, Year == 2011)
df1 <- subset(df1, Question == "Percent of adults aged 18 years and older who have obesity")
df1 <- df1[order(df1$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df1[i,4],df1[i+1,4],df1[i+2,4],df1[i+3,4],df1[i+4,4],df1[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_means <- cbind(unique(df1$Year),unique(df1$State), unique(df1$Question), round(x, digits = 1))
df_means <- as.data.frame(df_means)
df_long <- melt(df_means[order(df_means$V4),])
p <- ggplot(df_long, aes(x = V2, y = as.numeric(V4), fill = V4)) +
  scale_y_continuous(limits = c(0,35)) + 
  theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + 
  geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("") +
  ylab("Percent of Population") +
  coord_flip()

p
```

Below Table \@ref(tab:tab2), shows the states with the lowest proportions of obesity.
And Table \@ref(tab:tab3) gives the states with the highest obesity rates.

```{r tab2, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means2 <- df_means[order(df_means$V4),]
names(df.means2)[names(df.means2) == 'V2'] <- 'State'
names(df.means2)[names(df.means2) == 'V4'] <- 'Proportion'
df.new <- cbind(df.means2$State,df.means2$Proportion)
knitr::kable(head(df.new),booktabs = TRUE, align = "c", caption = "Lowest Obesity Rates By State") %>% 
kable_styling(full_width = F, position = "float_left") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab3, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means3 <- df_means[order(df_means$V4, decreasing = T),]
names(df.means3)[names(df.means3) == 'V2'] <- 'State'
names(df.means3)[names(df.means3) == 'V4'] <- 'Proportion'
df.new2 <- cbind(df.means3$State,df.means3$Proportion)
knitr::kable(head(df.new2),booktabs = TRUE, align = "c", caption = "Highest Obesity Rates by State") %>% 
kable_styling(full_width = F, position = "left") %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r fig2, echo = FALSE, fig.cap = "Bar plot of Obesity by State", fig.width=8,fig.height=8}
### Bar plot of Obesity by State ###
df2 <- subset(df, Year == 2019)
df2 <- subset(df2, Question == "Percent of adults aged 18 years and older who have obesity")
df2 <- df2[order(df2$State),]
x <- c()
i = 1
while (i < 312) {
  y = mean(c(df2[i,4],df2[i+1,4],df2[i+2,4],df2[i+3,4],df2[i+4,4],df2[i+5,4]))
  x <- c(x,y)
  i = i+6
}
df_m <- cbind(unique(df2$Year),unique(df2$State), unique(df2$Question), round(x, digits = 1))
df_m <- as.data.frame(df_m)
df_l <- melt(df_m[order(df_m$V4),])
p <- ggplot(df_l, aes(x = V2, y = as.numeric(V4), fill = V4)) +scale_y_continuous(limits = c(0,50)) + theme(legend.position="none", axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0)) + geom_bar(width = 0.8, stat = "identity", position = 'dodge') +
  xlab("") +
  ylab("Percent of Population")

@@

```{r tab4, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means4 <- df_m[order(df_m$V4),]
names(df.means4)[names(df.means4) == 'V2'] <- 'State'
names(df.means4)[names(df.means4) == 'V4'] <- 'Proportion'
df.new4 <- cbind(df.means4$State,df.means4$Proportion)
knitr::kable(head(df.new4),booktabs = TRUE, align = "c", caption = "Lowest Rates of Obesity by State") %>% 
kable_styling(full_width = F, position = "float_left") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab5, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df.means5 <- df_m[order(df_m$V4, decreasing = T),]
names(df.means5)[names(df.means5) == 'V2'] <- 'State'
names(df.means5)[names(df.means5) == 'V4'] <- 'Proportion'
df.new5 <- cbind(df.means5$State,df.means5$Proportion)
knitr::kable(head(df.new5),booktabs = TRUE, align = "c", caption = "Highest Rates of Obesity by State") %>% 
kable_styling(full_width = F, position = "left") %>%
kable_styling(latex_options = "HOLD_position")
```

@@

Below we now look at the proportion of state residents participating in aerobic activities for 150min or more per week as well as the proportion of residents participating in muscle strength training for at least 2 hours per week. We see in Table \@ref(tab:tab10) and Table \@ref(tab:tab11) some familiar states from the Obesity rate Tables \@ref(tab:tab4) and Table \@ref(tab:tab5). Namely Alabama which was one of the highest rates for Obesity in the country also has low rates of Aerobic activity.
```{r tab10, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means4 <- df8_means_150[order(df8_means_150$V4),]
names(df8.means4)[names(df8.means4) == 'V2'] <- 'State'
names(df8.means4)[names(df8.means4) == 'V4'] <- 'Proportion'
df8.new4 <- cbind(df8.means4$State,df8.means4$Proportion)
knitr::kable(head(df8.new4),booktabs = TRUE, align = "c", caption = "States with Lowest rates of Aerobic training") %>% 
kable_styling(full_width = F, position = "float_left") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab11, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means5 <- df8_means_150[order(df8_means_150$V4, decreasing = T),]
names(df8.means5)[names(df8.means5) == 'V2'] <- 'State'
names(df8.means5)[names(df8.means5) == 'V4'] <- 'Proportion'
df8.new5 <- cbind(df8.means5$State,df8.means5$Proportion)
knitr::kable(head(df8.new5),booktabs = TRUE, align = "c", caption = "States with Highest rates of Aerobic training") %>% 
kable_styling(full_width = F, position = "left") %>%
kable_styling(latex_options = "HOLD_position")
```

@@

```{r tab12, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means6 <- df8_means_muscle[order(df8_means_muscle$V4),]
names(df8.means6)[names(df8.means6) == 'V2'] <- 'State'
names(df8.means6)[names(df8.means6) == 'V4'] <- 'Proportion'
df8.new6 <- cbind(df8.means6$State,df8.means6$Proportion)
knitr::kable(head(df8.new6),booktabs = TRUE, align = "c", caption = "States with Lowest rates of Muscle Training") %>% 
kable_styling(full_width = F, position = "float_left") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r tab13, echo = FALSE, fig.pos = 'H'}
### Buidling Excerpt ###
df8.means7 <- df8_means_muscle[order(df8_means_muscle$V4, decreasing = T),]
names(df8.means7)[names(df8.means7) == 'V2'] <- 'State'
names(df8.means7)[names(df8.means7) == 'V4'] <- 'Proportion'
df8.new7 <- cbind(df8.means7$State,df8.means7$Proportion)
knitr::kable(head(df8.new7),booktabs = TRUE, align = "c", caption = "States with Highest rates of Muscle training") %>% 
kable_styling(full_width = F, position = "left") %>%
kable_styling(latex_options = "HOLD_position")
```
The interesting thing here is we see Montana and Vermont both with very high rates of Aerobic Activity, likely attributed to these states being far more rural then the average state, allowing more opportunity for outdoor activities. However again on the low end 
\newpage
